### 2023-05-29 paper/paper.tex
Updates

% \begin{declaration}
% 	\addchaptertocentry{\authorshipname} % Add the declaration to the table of contents
% 	\noindent I, \authorname, declare that this thesis titled, \enquote{\ttitle} and the work presented in it are my own. I confirm that:
%
% 	\begin{itemize}
% 		\item This work was done wholly or mainly while in candidature for a research degree at this University.
% 		\item Where any part of this thesis has previously been submitted for a degree or any other qualification at this University or any other institution, this has been clearly stated.
% 		\item Where I have consulted the published work of others, this is always clearly attributed.
% 		\item Where I have quoted from the work of others, the source is always given. With the exception of such quotations, this thesis is entirely my own work.
% 		\item I have acknowledged all main sources of help.
% 		\item Where the thesis is based on work done by myself jointly with others, I have made clear exactly what was done by others and what I have contributed myself.\\
% 	\end{itemize}
%
% 	\noindent Signed:\\
% 	\rule[0.5em]{25em}{0.5pt} % This prints a line for the signature
%
% 	\noindent Date:\\
% 	\rule[0.5em]{25em}{0.5pt} % This prints a line to write the date
% \end{declaration}
%
% \cleardoublepage
\todo{Enable}

@@

% \vspace*{0.2\textheight}
%
% \noindent\enquote{\itshape Thanks to my solid academic training, today I can write hundreds of words on virtually any topic without possessing a shred of information, which is how I got a good job in journalism.}\bigbreak
%
% \hfill Dave Barry
\todo{Enable}

@@

	Current state-of-the-art techniques occasionally fail to accurately estimate
	the camera parameters for wide-angle lenses, as most of the algorithms assume
	lenses with medium to small distortion. Partially it occurs due to extreme
	distortion at the edges of the image, which poses additional challenges to
	feature detection algorithms. We propose a novel approach for detecting
	additional features on the imaged calibration pattern using intermediate
	camera calibration. Utilizing the prior information about the calibration
	pattern's geometry, we can estimate the possible positions of the previously
	undetected features. Those features are filtered using the binary classifier,
	and the remaining ones are used to further constrain the camera calibration.
	The proposed method consists of three key steps: \((1)\) feature
	detection and estimation of the lattice geometry, \((2)\) initial camera
	calibration by solving the two-steps linear minimization problem, and \((3)\)
	estimation the possible positions of the undetected features by projecting the
	imputed and extended lattice geometry onto the image plane, and filtering them
	using the binary classifier.

@@

% \begin{acknowledgements}
% 	\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents
% 	The acknowledgments and the people to thank go here, don't forget to include your project advisor\ldots
%
% 	\noindent If you was supported with the scholarship, please thank to your donor organization or a person who supported you.
% \end{acknowledgements}
\todo{Enable}

>>>>

\begin{declaration}
	\addchaptertocentry{\authorshipname} % Add the declaration to the table of contents
	\noindent I, \authorname, declare that this thesis titled, \enquote{\ttitle} and the work presented in it are my own. I confirm that:

	\begin{itemize}
		\item This work was done wholly or mainly while in candidature for a research degree at this University.
		\item Where any part of this thesis has previously been submitted for a degree or any other qualification at this University or any other institution, this has been clearly stated.
		\item Where I have consulted the published work of others, this is always clearly attributed.
		\item Where I have quoted from the work of others, the source is always given. With the exception of such quotations, this thesis is entirely my own work.
		\item I have acknowledged all main sources of help.
		\item Where the thesis is based on work done by myself jointly with others, I have made clear exactly what was done by others and what I have contributed myself.\\
	\end{itemize}

	\noindent Signed:\\
	\rule[0.5em]{25em}{0.5pt} % This prints a line for the signature

	\noindent Date:\\
	\rule[0.5em]{25em}{0.5pt} % This prints a line to write the date
\end{declaration}

\cleardoublepage

@@

% \vspace*{0.2\textheight}
%
% \noindent\enquote{\itshape Thanks to my solid academic training, today I can
% write hundreds of words on virtually any topic without possessing a shred of
% information, which is how I got a good job in journalism.}\bigbreak
%
% \hfill Dave Barry

@@

	Current state-of-the-art techniques occasionally fail to accurately estimate
	the camera parameters for wide-angle lenses, as most of the algorithms assume
	lenses with medium to small distortion. Partially it occurs due to extreme
	distortion at the edges of the image, which poses additional challenges to
	feature detection algorithms. We propose a novel approach for detecting
	additional features on the imaged calibration pattern using intermediate
	camera calibration. Utilizing the prior information about the calibration
	pattern's geometry, we can estimate the possible positions of the previously
	undetected features. Those features are filtered using the binary classifier,
	and the remaining ones are used to further constrain the camera calibration.
	The proposed method consists of three key steps: \((1)\) feature
	detection and estimation of the lattice geometry, \((2)\) initial camera
	calibration by solving the two-step linear minimization problem, and \((3)\)
	estimation of the possible positions of the undetected features by projecting the
	imputed and extended lattice geometry onto the image plane, and filtering them
	using the binary classifier.

@@

\begin{acknowledgements}
	\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents
  I wish to thank the Armed Forces of Ukraine for protecting us. Thanks to those
  brave people I was able to study and work on this thesis. I want to thank my
	% The acknowledgments and the people to thank go here, don't forget to include your project advisor\ldots

	% \noindent If you was supported with the scholarship, please thank to your donor organization or a person who supported you.
\end{acknowledgements}
